Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
adding terminology.
add comment.
Talking HP as evidence.

Haskell programmers, however, tend to rely on the type system too much.  They
tend to write less test code than programmers of other programming languages.

\begin{quote}
    \emph{we need evidence to support this.}
\end{quote}

This also means that typical usage examples are not provided by test code.

@@

\item[documentation]
    Explanation of functions.
\end{description}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

\appendix

\section{Package Survey}

TBD

>>>>

Haskell programmers, however, is apt to rely on the type system too much
and tend not to write test code.
For example, Haskell Platform 2011.4.0.0 contains
TBD packages but TBD of them have no test code.
Lacking test code also means that typical usage examples are not provided.

@@

\item[user documentation]
    TBD: Explanation of functions.
\item[code documentation]
    TBD: Explanation of functions.

\end{description}

@@

\begin{quote}
@sol: I used \verb|rev| just because it is short.
Actually I used \verb|reverse| once but it is overflowed
in the right hand side.
\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \section{Conclusion}

%% \appendix

%% \section{Package Survey}

%% TBD
